The impact of cosmic variance on simulating weak lensing surveys

### 2015-02-26 Writeup/reply.tex
beginning to edit referee response, did not get far

\newcommand{\rachel}[1]{\textrm{\textbf{Rachel: #1}}}
\newcommand{\arun}[1]{\textrm{\textcolor{red}{Arun: #1}}}
\newcommand{\claire}[1]{\textrm{\textcolor{blue}{Claire: #1}}}

@@

\begin{letter}{Ms. Anna Evripidou\\ Assistant Editor\\ 'Monthly Notices' and 'Geophysical Journal International' \\
Royal Astronomical Society}

@@

We are very grateful to the referee for the careful reading of the manuscript.
We resubmit a modified version taking care of the comments and criticisms of the referee; we have also
used this opportunity to make a careful reading and fix typos and clarify potentially confusing sentences. 
Please find below a point-by-point response to the referee report.

@@

We thank the referee for carefully reading our manuscript and for the acknowledgment that our work is of interest
and suitable for MNRAS and for finding our approach appropriate. We are grateful for the pointers for improving the presentation; and for the clarifications. 
Below we address the specific issues raised.

>>>>

\newcommand{\rachel}[1]{\textrm{\textcolor{green}{Rachel: #1}}}
\newcommand{\arun}[1]{\textrm{\textcolor{red}{Arun: #1}}}
\newcommand{\claire}[1]{\textrm{\textcolor{blue}{Claire: #1}}}

@@

\rachel{A basic comment about format: the MNRAS system will force you to upload a separate reply to
  the editor and to the authors.  So having it together in a single compiled PDF is not convenient.
  You should split it up into two files.  Also I'm not sure the system will let you enter your
  comments to the editor as a PDF, it might have to be text.}

\begin{letter}{Ms. Anna Evripidou\\ Assistant Editor\\ Monthly Notices of the 
Royal Astronomical Society}

@@

We are very grateful to the referee for the careful reading of the manuscript.
We resubmit a modified version taking care of the comments and criticisms of the referee, plus
additional minor changes that are also explained in the report to the referee.

Please find below a point-by-point response to the referee report.

@@

We thank the referee for carefully reading our manuscript and for the acknowledgment that our work is of interest
and suitable for MNRAS. We are grateful for the pointers for improving the presentation and
explanation of our work. 
Below we address the specific issues raised.
